data_cleaning

### 2015-11-26 analysis/exp_data_clean.Rmd
added total to e11 prag listener - need to figure out how to add CI's. Why is this hard?

## Cleaning / formatting - output
```{r}
# Preliminary data cleaning
# -------------------------
ms <- d %>%
  group_by(degree, scale) %>%
  mutate(n = n()) %>%
  group_by(degree, scale, stars) %>%
  summarise(listener.p = n() / n[1])
# Output to CSV
# --------------
write.csv(ms, "../models/model_data/L1_e11.csv", row.names=FALSE)
```

>>>>

## Cleaning / formatting - output
```{r}
# Preliminary data cleaning
# -------------------------
ms <- d %>%
  group_by(degree, scale) %>%
  mutate(n = n()) %>%
  group_by(degree, scale, stars) %>%
  summarise(listener.p = n() / n[1],
            total = sum(stars == stars))

# Output to CSV
# --------------
#write.csv(ms, "../models/model_data/L1_e11.csv", row.names=FALSE)
```
